---
title: "Eating Out"
author: "Riley Wheeler"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "Summer 2022"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The data comes from the 1998 General Social Survey answer this question

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

# METHODS 

The response variable is categorical: Dine out last week? y/n

Explanatory variable is race, also a categorical varaable so we use cat~cat.

Inference: chi-squared and fischer exact tests.

# Descriptive Summary

## Graphical Summary

### Barchart

```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```

It appears that white people eat out much more than other races, while blacks eat out in similar frequency as other.

## Numarical Summary

```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```

This table shows that white people eat out more than other and black people by about a 15% margin.

# Results

## Inferrential Results

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

The chi-squared test shows that white people eat significantly more fast food than blacks or other races. The P values of the chi-squared and the Fischer exact tests are 2.287e-06 and 4.633e-06 which are both far less than .05 so we must reject the null hypothesis. 

```{r}
fisherXY(mydata$race,mydata$eatout, printAll = TRUE)
```
According to the Fischer exact test, there is large disparity between whites and blacks in eating out. The same goes for whites and other since the P value is .007 and 1.183e-05. Between blacks and other however, the p value is greater than .05 so there is not much difference. The odds ratio shows that whites are nearly twice as likely (1.902047)to eat out than blacks. 

# Discussion and Conclusion

The original question was: is there a statistical difference between at least two races with the Frequency of eating out? The analysis of the data reveals that white people are significantly more likely to eat out than blacks or other races. Between blacks and other races, there is not much difference regarding frequency of eating out so there is no correlation. We must reject the null hypothesis that There is no difference among the various races with frequency of eating out because whites eat nearly double the fast food that any other race does.





